Foremost, I would like to express my sincere gratitude to my advisor 
Prof. Ying Wu for the continuous support of my Ph.D study and research,
for his patience, motivation, enthusiasm, and immense knowledge.
His guidance helped me in all the time of research and writing of this thesis.
I could not have imagined having a better advisor and mentor for my Ph.D study.\\

Besides my advisor, I would like to thank the rest of my thesis
committee: Prof. Aggelos K.Katsaggelos, Prof. Thrasyvoulos N.Pappas, and
Dr. James Crenshaw, for their encouragement, insightful comments, and hard questions.\\

My sincere thanks also goes to Dr. James Crenshaw, Dr. Senthil Periaswamy,
and Dr. Qiong Liu, for offering me the summer internship opportunities in
their groups and leading me working on diverse exciting projects.\\

I thank my fellow labmates in Northwestern Vision Group: Gang Hua, Ting Yu,
Zhimin Fan, Shengyang Dai, Junsong Yuan, Jiang Xu, Jialue Fan, and Neelabh Gupta,
for the stimulating discussions, for the sleepless nights we were working together
before deadlines, and for all the fun we have had in the last four years.
Also I thank my friends in Tsinghua University: Chen Fan, Wensheng Wang, Bo Qin, Xiwei Wang,
Yonggang Zhao, Hua Chen, Junlin Li, and Rui Zhou. In particular, I am grateful to
Dr. Chen Fan for enlightening me the first glance of research.\\

Last but not the least, I would like to thank my family: my parents Siyu Yang and
Xiaolan Ding, for giving birth to me at the first place and supporting me spiritually
throughout my life.\\
